Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-04 thesis/paper.tex
Started disc RQ2

\subsection{RQ1.1}

@@

\subsection{RQ2}

\noindent
\textbf{Feedback system  }
Something that is very important and might be overlooked in API development/evolution

\smallskip \noindent
\textbf{Why don't all theories apply?  }
Try explain what the reason might be, by comparing APIs to normal systems. 
(Complexity and quality) These apply, but it seems that they are not very important compared to for exmaple functionality. Maybe they are true to a lesser extent compared to normal systems. 
This is interesting becaues it means one cannot assume that APIs are e-type systems and it cannot be compared to ``normal'' systems in some cases.

\smallskip \noindent
\textbf{The true ones  }

List the ones that we found a lot of evidence  (the most true: 6,7) (1, 3, 5) and explain why they are true by linking it to RQ1 results

>>>>

\newpage

\subsection{Discussion RQ1.1}

@@

\newpage
\subsection{Discussion RQ2}

\noindent
\textbf{A majority of the laws apply  }
Sufficient evidence was found for the laws of Continuing Change, Self Regulation, Conservation of Familiarity, Continuing Growth and Feedback System to establish that they apply to APIs. The most major explanation for this that a large part of the introduced changes were related to functionality. It is especially interesting to note that the laws of Self Regulation and Conservation of Familiarity perfectly match the API explored in this paper.

\smallskip \noindent
\textbf{Two laws kinda apply  }
The laws of Increasing Complexity and Declining Quality were found to apply to APIs, but that the extent to which they apply might not be as significant for APIs compared to other types of systems. The reason that this doubt exists is that these motivations could were only secondary to the motivations of increased functionality. An alternative explanation for these laws being of lesser significance in APIs could be that the general inertia to modify APIs which exists \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} might overshadow (!!!wording) the need to increase simplicity and quality.

\smallskip \noindent
\textbf{One law does not apply}
Strong evidence was found which suggests that the law of Conservation of Organisational Stability does not apply to APIs.

This is interesting becaues it means one cannot assume that APIs are e-type systems and it cannot be compared to ``normal'' systems in some cases. 
\smallskip \noindent
\textbf{Feedback system  }
Something that is very important and might be overlooked in API development/evolution

\newpage
